Automated Formal Synthesis\\ of Safe Digital Controllers for Continuous Plants

### 2018-05-11 automatica/paper.tex
section 6

As discussed in \note{Section~\ref{sec:}}, 
the models we consider have to account for errors from several sources: 
the numerical error introduced by the finite precision used to represent the plant \note{(and its operations)},  
the error introduced by the ADC\note{/DAC?} conversion, 
and the error introduced by the limited precision used to represent the controller. 
First we consider the numerical errors introduced by the finite precision numbers (either fixed or floating point) used to model the plant and used by the digital controller. 
Then we account for the quantization errors introduced by the ADC\note{/DAC?}.

\subsection{Errors due to numerical representation}
First consider the case where we use fixed-point representations, and synthesise fixed-point controllers.

@@

\subsection{Notation}
In this paper we will use $\mathcal{F}_{\langle I_c,F_c \rangle}(x)$ to denote a real
number $x$ represented at the fixed-point precision of the controller, and
$\mathcal{F}_{\langle I_p,F_p \rangle}(x)$ to denote a real number $x$
represented at the fixed-point precision of the plant model ($I_c$ and $F_c$
are determined by the controller.  We pick $I_p$ and $F_p$ for our synthesis
such that $I_p \geq I_c$ and $\allowbreak F_p \geq F_c$).  Thus any
mathematical operations in our modelled digital controller will be in the
range of $\mathcal{F}_{\langle I_c,F_c \rangle}$, and all other calculations
in our model will be carried out in the range of $\mathcal{F}_{\langle
I_p,F_p \rangle}$.  The physical plant operates in the reals, which means
our verification phase must also account for the numerical error and
quantization errors caused by representing the physical plant at the finite
precision $\mathcal{F}_{\langle I_p,F_p \rangle}$.

\subsection{Floating point representation}

>>>>

As discussed in \note{Section~\ref{sec:}}, 
the models we consider have to account for errors from several sources: 
the numerical error introduced by the finite precision used to represent the plant \note{(and its operations)},  
the error introduced by the ADC\note{/DAC?} conversion, 
and the error introduced by the limited precision used to represent the controller. 
First we consider the numerical errors introduced by the finite precision numbers (either fixed- or floating-point) used to model the plant and used by the digital controller. 
Then we account for the quantization errors introduced by the ADC\note{/DAC?}.

\subsection{Errors due to numerical representations}

Let us first consider the case of fixed-point representation of the model, 
and of synthesis of fixed-point controllers.

@@

\subsection{Notations}

\note{If these notations are used in earlier Sections, shall we anticipate the paragraph to the preliminaries? }

In this paper we will use $\mathcal{F}_{\langle I_c,F_c \rangle}(x)$ to denote a real
number $x$ represented at the fixed-point precision of the controller, and
$\mathcal{F}_{\langle I_p,F_p \rangle}(x)$ to denote a real number $x$
represented at the fixed-point precision of the plant model ($I_c$ and $F_c$
are determined by the controller.  We pick $I_p$ and $F_p$ for our synthesis
such that $I_p \geq I_c$ and $\allowbreak F_p \geq F_c$ \note{why is this reasonable?}).  
Thus any mathematical operations in our modelled digital controller will be in the
range of $\mathcal{F}_{\langle I_c,F_c \rangle}$, and all other calculations
in our model will be carried out in the range of $\mathcal{F}_{\langle
I_p,F_p \rangle}$.  The physical plant operates in the reals, which means
our verification phase must also account for the numerical error and
quantization errors caused by representing the physical plant at the finite
precision $\mathcal{F}_{\langle I_p,F_p \rangle}$.

\note{also introduce notations for floats?}

\subsection{Floating-point representation}

\note{Notice that this notation is different than the one used in the results section. pls fix. }
